Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-13 ms.qmd
Added R2 in...

# Observed by Lat/long
  ggplot(data = data_w_pred, aes(y = effect_size, x = lat.y)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()

  ggplot(data = data_w_pred, aes(y = effect_size, x = long.x)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()

>>>>

# Observed by Lat/long
  ggplot(data = data_w_pred, aes(y = effect_size, x = lat.y)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Observed Effect Size") + theme_classic()

  ggplot(data = data_w_pred, aes(y = effect_size, x = long.x)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Observed Effect Size") + theme_classic()

# How much variation does this model explain. Need to do this manually because function doesn't seme to work on the model object. We need to remember that predcit will include random effect variances so we may need to exclude this
  re_post <- posterior_samples(model5_bayes, pars = "^sd_")
  v_fix <- apply(predict(model5_bayes, summary = FALSE), 1, function(x) var(x))

# Extract the random effect variances
  v_trait <- re_post$sd_trait__Intercept^2
    v_spp <- re_post$sd_spp__Intercept^2
    v_phy <- re_post$sd_species_full__Intercept^2
    v_std <- re_post$sd_record_num__Intercept^2
      v_r <- re_post$sd_obs__Intercept^2

# Lets get the total variance for the random effects only
  tot_re <- v_trait + v_spp + v_phy + v_std + v_r

# Now, calculate r2 marginal, by subtracting the random effect variance from the fixed effect variance (which includes random effects). Need to check this as it may not be this intuitive
  r2 <- (v_fix - tot_re) / (v_fix)

  mean(r2) # Seems a bit high 
  quantile(r2, probs = c(0.025, 0.975))
